\documentclass{scrartcl}	% classe article di KOMA
\reversemarginpar
\newcommand{\MarginDate}[1]{\marginpar{\raggedleft\itshape\small#1}\\}
\newcommand{\MarginDateb}[1]{\marginpar{\raggedleft\itshape\small#1}}
%\usepackage[latin1]{inputenc}	% la codifica di input
%\usepackage[T1]{fontenc}	% la codifica dei font
\usepackage[LabelsAligned]{currvita}	% un buon pacchetto per CV
\usepackage[nochapters]{classicthesis} % stile ClassicThesis
\usepackage[a4paper, footskip=0.5cm, top=2cm, bottom=2cm, left=5cm, right=5cm]{geometry}
\usepackage{url}	% per gli indirizzi Internet
\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}}
\renewcommand{\cvlistheadingfont}{\large}
\renewcommand{\cvlabelfont}{\qquad}
\setlength{\parindent}{-0.5cm}
% PDF SETUP
\usepackage{multicol}
\usepackage{color} 
\definecolor{myblue}{rgb}{0,0.2,0.4}
\date{}
% Setup hyperref package, and colours for links, text and headings
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage{hyperref} 		
\hypersetup{	
  colorlinks,
  breaklinks,
  urlcolor=myblue, 
  linkcolor=myblue,
  pdftitle={Robert Myhill - Curriculum Vitae},
  pdfauthor={Robert Myhill}}
\usepackage{eurosym}
\newlength{\datebox}\settowidth{\datebox}{\today}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 


\newcommand{\NewWorkExperience}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\textit{#1}}\hspace{1.5em} #2 #3%
\vspace{0.5em}\\}
\newcommand{\SubHeading}[2]{\noindent\hangindent=2em\flushleft #1 #2%
\vspace{0.5em}\\}
\newcommand{\Description}[1]{\hangindent=2em\footnotesize{#1}\par\normalsize}
\newcommand{\Heading}[1]{\hangindent=0em\flushleft\spacedlowsmallcaps{#1}}
\newcommand{\Sep}{\vspace{2em}}
\begin{document}
\thispagestyle{empty}
\begin{cv}

\begin{center}
\textsc{Curriculum Vitae}
\vspace{8pt}
\hrule
\vspace{8pt}
\LARGE \textsc{Robert Myhill}
\end{center}
\vspace{8pt}
\flushleft{Department of Earth Sciences} \\
University of Cambridge \\
Bullard Laboratories \\
Madingley Rise \\
Cambridge, CB3 0EZ \\
UK \\

\vspace{1.5em}
\Heading{Contact Details}
\vspace{0.5em}

\NewWorkExperience{phone}{+44 (0)7841 714164}{}
\NewWorkExperience{fax}{+44 (0)1223 360779}{}
\NewWorkExperience{email}{\href{mailto:rm438@cam.ac.uk}{rm438@cam.ac.uk}}{}
%%\NewWorkExperience{\textsc{url}}{\href{http://www.esc.cam.ac.uk/people/research-students/bob-myhill}{http://www.esc.cam.ac.uk/people/research-students/bob-myhill}}\\ 


\vspace{1.5em}
\Heading{Education}
\vspace{0.5em}

\NewWorkExperience{Current}{PhD Research Student at}{U. Cambridge}
\Description{
Researching \MarginDateb{The Mechanisms of Deep Focus Earthquakes} the causes of earthquakes at depths greater than 300 km through an integrated analysis of seismic distributions, focal mechanisms and \emph{P-T} regimes within which these events occur. I aim to combine this analysis with previous work to elucidate aspects of the interaction between subducting plates and the upper-lower mantle boundary.\\
\emph{Advisors: Dan McKenzie and Keith Priestley}.
}
\Sep

\Description{
\textsc{MSci + BA} \MarginDateb{2004-2008} Peterhouse, University of Cambridge, Class of 2008. \\
Natural Sciences (Physical; 4 years).\\
Part III: First Class. 1/36 in Class (Geological Sciences).\\
Part II: First Class. 1/39 in Class (Geological Sciences).\\
Part IB: First Class (Maths, Stratigraphic Geology, Mineralogy, Petrology).\\
Part IA: First Class (Geology, Maths, Physics, Chemistry).
}



\vspace{1.5em}
\Heading{Selected grants and awards}
\vspace{0.5em}

\Description{
The \MarginDateb{2008} Hugo de Balsham Prize for Exceptional Academic Distinction.\\
The Harkness Scholarship (first-placed Finalist in Geological Sciences, Cambridge University).\\
The Huppert Prize in Geophysics.\\
The Henry Wilkinson Cookson Senior Scholarship \MarginDateb{2007} in Natural Sciences.\\
The John Reekie Memorial Prize for the best geological fieldwork-based thesis submitted for the first degree at the Department of Earth Sciences.\\
Peterhouse College Prizes and Scholarships \MarginDateb{2005-2008}.\\
Departmental Field Mapping Prizes \MarginDateb{2004-2007}\\ (Arran, Sedbergh, Dorset and Cornwall, Greece).\\
St. John Ambulance Grand Prior Award. \MarginDate{2003}
}

\clearpage
\vspace{1.5em}
\Heading{Publications and presentations}
\vspace{0.5em}


\SubHeading{Peer-reviewed journal articles}{}
\Description{
R. Myhill, D. McKenzie, K. Priestley, \MarginDateb{2010} ``Clustering of deep focus earthquakes in the southwest Pacific''. \\
\emph{Submitted to EPSL.}\\
R. Myhill, \MarginDateb{2008} ``Constraints on evolution of the Mesohellenic Ophiolite from sub-ophiolitic metamorphic rocks''. \\
\emph{GSA Special Publication, accepted.}\\
A. Rassios, Y. Dilek, R. Myhill, D. Ghikas, A. Mpatsi, \MarginDateb{2008} ``Melange Formations beneath the Pindos Basin Ophiolites, Northern Greece: Evidence of an “active,” rapid decollement emplacement surface''. \\
\emph{GSA Special Publication, accepted.}
}

\Sep

\SubHeading{Presentations}{}
\Description{
``Clustering of deep focus \MarginDateb{2009} earthquakes in the southwest Pacific''. \emph{Poster presentation, AGU Fall Meeting.}\\
``Faulting 300 kilometers down: \MarginDateb{2009} The mystery of deep focus earthquakes''. \emph{Magdalene Parlour Talk.}\\
``Deep focus earthquakes''. \emph{First year PhD presentation.}\\
``The significance of high temperature \MarginDateb{2008} low pressure rocks beneath the Mesohellenic Ophiolite''. \emph{Poster presentation, IGME Field Symposium: Ophiolites 2008.}\\
IGME Field Symposium: Ophiolites 2008. \emph{Field Guide.}\\
K\"{o}ln undergraduate field trip to Greece. \emph{1-day Guest Field Guide.}
}


\vspace{1.5em}
\Heading{Relevant Experience}
\vspace{0.5em}


\Description{
Masters Thesis at U. Cambridge. \MarginDateb{06/07-01/08} Metamorphic Development beneath the Mesohellenic Ophiolite. I obtained a high First (80\%) for this project.\\
\emph{Advisor: Dr. Timothy Holland, Cambridge University.}\\
}

\Description{
Bachelors Thesis at U. Cambridge. \MarginDateb{06/06-01/07} Independent mapping project and industrial work experience: Vourinos, Northern Greece. I obtained the top First in the year for this project (80\%).\\
\emph{Advisors: Dr. Alan Smith, Cambridge University and Dr. Anne Rassios, Greek Institute of Geology and Mineral Exploration (IGME).}
}

\Description{
Voluntary Worker, British Geological Survey. \MarginDateb{07/05-08/05} Paid appointment for part of a national environmental survey (The Tellus Project) completed in 2006.\\
\emph{Advisors: Louise Ander, Sean Quigley, Sophia Passmore (British Geological Survey).}
}

\Description{
Supervisions \MarginDateb{2008-present}given in the following courses: \emph{IA Geology; IB Hydrosphere, Tectonics and Structural Geology; II/III Essay Skills.}\\
Demonstrated in the following courses: \emph{IB Tectonics and Structural Geology; II/III Tectonics, Seismology (partial).}\\
Field Demonstrator: \emph{Ketton (IA), Arran (IA), Sedbergh (IB)}.\\
}

\Description{
250+ \MarginDateb{2005-present}days fieldwork experience (as of 01/10/09) as demonstrator, field guide, employee, researcher and student.\\
\emph{(Locations include: Ireland, Iceland, Greece, Dorset, Cornwall, Sedbergh, and the Isles of Arran and Skye.)}
}

\clearpage
\vspace{1.5em}
\Heading{Other Experience}
\vspace{0.5em}

\Description{
Treasurer, \MarginDateb{2010-2011} Magdalene Middle Common Room.\\
Duties Coordinator, Cambridge LINKS (St. John Ambulance).\\
Vice President and President; \MarginDateb{2006-2008} Sedgwick Club (Geological Society of the University of Cambridge).\\
Divisional Secretary, Chairman and Treasurer; \MarginDateb{2005-2008} Cambridge University Association Football League.\\
Time Truck \MarginDateb{2006-2007} (Cambridge Geological Outreach) Committee Member.\\
Volunteer \MarginDateb{2005-present} for Time Truck.\\
Team Member of Science and Engineering Experiments for Kids, Cambridge: Science Outreach for local schools.\\
}

\vspace{1.5em}
\Heading{Skills}
\vspace{0.5em}

\Description{
\begin{itemize}
\item Competent user of \LaTeX, Microsoft and Serif Office programs and basic knowledge of Access.
\item Experience of FORTRAN, C, C++ languages, BASH and HTML scripting and use of the OpenGL API.
\item Over 300 hours experience with THERMOCALC (a thermobarometry program based on Gibbs Energy minimisation).
\item First Aider with St John Ambulance (First Aid at Work expires 12/2012).
\item Basic Training in Manual Handling, Radio Communication, Fire Safety.
\end{itemize}
}

\vspace{1.5em}
\Description{Geology\ \ $\cdotp$\ \ Music\ \ $\cdotp$\ \ First Aid\ \ $\cdotp$\ \  Programming\ \ $\cdotp$\ \  Foreign Travel\ \ $\cdotp$\ \  Greek\MarginDate{Interests}}

\vspace{1.5em}
\Heading{Referees}

\Description{
\begin{multicols}{2}{
PhD project supervisor\\
Prof. Dan McKenzie\\
Bullard Laboratories,\\
University of Cambridge,\\
Madingley Rise,\\
Cambridge.\\
CB3 0EZ.\\
UNITED KINGDOM.\\
\texttt{+44 (0)1223 337191}\\
\href{mailto:mckenzie@madingley.org}{mckenzie@madingley.org}.\\
\columnbreak
Part III project supervisor\\
Dr. Timothy Holland\\
Dept. of Earth Sciences,\\
University of Cambridge,\\
Downing Street,\\
Cambridge.\\
CB2 3EQ.\\
UNITED KINGDOM.\\
\texttt{+44 (0)1223 333453}\\
\href{mailto:tjbh@esc.cam.ac.uk}{tjbh@esc.cam.ac.uk}.\\
}
\end{multicols}
}

\vfill

% FILL IN THE FULL URL TO YOUR CV
\begin{center}
{\footnotesize \href{http://www.srcf.ucam.org/~rm438/files/CV.pdf}{http://www.srcf.ucam.org/$\sim$rm438/files/CV.pdf}\\
Last updated: \today}
\end{center}



\enlargethispage{\baselineskip}
\end{cv}
\end{document}
