\documentclass{scrartcl}	% classe article di KOMA
\reversemarginpar
\newcommand{\MarginDate}[1]{\marginpar{\raggedleft\itshape\small#1}\\}
\newcommand{\MarginDateb}[1]{\marginpar{\raggedleft\itshape\small#1}}
%\usepackage[latin1]{inputenc}	% la codifica di input
%\usepackage[T1]{fontenc}	% la codifica dei font
\usepackage[LabelsAligned]{currvita}	% un buon pacchetto per CV
\usepackage[nochapters]{classicthesis} % stile ClassicThesis
\usepackage[a4paper, footskip=0.5cm, top=2cm, bottom=2cm, left=5cm, right=5cm]{geometry}
\usepackage{url}	% per gli indirizzi Internet
\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}}
\renewcommand{\cvlistheadingfont}{\large}
\renewcommand{\cvlabelfont}{\qquad}
\setlength{\parindent}{-0.5cm}
% PDF SETUP
\usepackage{multicol}
\usepackage{color} 
\definecolor{myblue}{rgb}{0,0.2,0.4}
\date{}
% Setup hyperref package, and colours for links, text and headings
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage{hyperref} 		
\hypersetup{	
  colorlinks,
  breaklinks,
  urlcolor=myblue, 
  linkcolor=myblue,
  pdftitle={Robert Myhill - Curriculum Vitae},
  pdfauthor={Robert Myhill}}
\usepackage{eurosym}
\newlength{\datebox}\settowidth{\datebox}{\today}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 


\newcommand{\NewWorkExperience}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\textit{#1}}\hspace{1.5em} #2 #3%
\vspace{0.5em}\\}
\newcommand{\SubHeading}[2]{\noindent\hangindent=2em\flushleft #1 #2%
\vspace{0.5em}\\}
\newcommand{\Description}[1]{\hangindent=2em\footnotesize{#1}\par\normalsize}
\newcommand{\Heading}[1]{\hangindent=0em\flushleft\spacedlowsmallcaps{#1}}
\newcommand{\Sep}{\vspace{2em}}
\begin{document}
\thispagestyle{empty}
\begin{cv}

\begin{center}
\textsc{Curriculum Vitae}
\vspace{8pt}
\hrule
\vspace{8pt}
\LARGE \textsc{Robert Myhill}
\end{center}
\vspace{8pt}
\flushleft{Department of Earth Sciences} \\
University of Cambridge \\
Bullard Laboratories \\
Madingley Rise \\
Cambridge, CB3 0EZ \\
UK \\

\vspace{1.5em}
\Heading{Contact Details}
\vspace{0.5em}

\NewWorkExperience{phone}{+44 (0)7841 714164}{}
\NewWorkExperience{fax}{+44 (0)1223 360779}{}
\NewWorkExperience{email}{\href{mailto:rm438@cam.ac.uk}{rm438@cam.ac.uk}}{}
%%\NewWorkExperience{\textsc{url}}{\href{http://www.esc.cam.ac.uk/people/research-students/bob-myhill}{http://www.esc.cam.ac.uk/people/research-students/bob-myhill}}\\ 


\vspace{1.5em}
\Heading{Personal Data}
\vspace{0.5em}

\NewWorkExperience{DOB}{16 March 1986}{}
\NewWorkExperience{Nationality}{British}{}

\vspace{1.5em}
\Heading{Education}
\vspace{0.5em}

\NewWorkExperience{Current}{PhD Research Student at}{U. Cambridge}
\Description{
Researching \MarginDateb{The Mechanisms of Deep Focus Earthquakes} the causes of earthquakes at depths greater than 300 km through an integrated analysis of seismic distributions, focal mechanisms and \emph{P-T} regimes within which these events occur. I aim to combine this analysis with previous work to elucidate aspects of the interaction between subducting plates and the upper-lower mantle boundary.\\
\emph{Advisors: Dan McKenzie and Keith Priestley}.
}
\Sep

\Description{
\textsc{MSci + BA} \MarginDateb{2004-2008} Peterhouse, University of Cambridge, Class of 2008. \\
Natural Sciences (Physical; 4 years).
}

\Description{
Part \MarginDateb{2007-2008} III: First Class. 1/36 in Class (Geological Sciences).
}

\Description{
Part \MarginDateb{2006-2007} II: First Class. 1/39 in Class (Geological Sciences).
}

\Description{
Part \MarginDateb{2005-2006} IB: First Class (Maths, Stratigraphic Geology, Mineralogy and Petrology).
}

\Description{
Part \MarginDateb{2004-2005} IA: First Class (Geology, Maths, Physics, Chemistry).
}

\Description{
Sir \MarginDateb{1999-2004} John Leman High School, Beccles.\\
5 A grades at AS level, converted to 5 A grades at A2 level. (Physics, Chemistry, Mathematics, Further Mathematics, General Studies).
}
\Sep
\clearpage
\vspace{1.5em}
\Heading{Grants and awards}
\vspace{0.5em}

\Description{
The \MarginDateb{2008} Hugo de Balsham Prize for Exceptional Academic Distinction.\\
Peterhouse College Prize.\\
Harkness Scholarship (first-placed Finalist in Geological Sciences, Cambridge University).\\
Huppert Prize in Geophysics (awarded for a high quality essay in geophysics).\\
Cambridge University NERC Studentship 2008-11 (accepted).\\
Open University NERC Studentship (with CASE Award; declined).\\
Oxford University NERC Studentship (with CASE Award; declined).\\
Departmental Field Mapping Prizes \MarginDateb{2004-2007}\\ (Arran, Sedbergh, Dorset and Cornwall, Greece).\\
The Henry Wilkinson Cookson Senior Scholarship \MarginDateb{2007} in Natural Sciences.\\
The John Reekie Memorial Prize for the best geological fieldwork-based thesis submitted for the first degree at the Department of Earth Sciences.\\
Peterhouse Senior Scholarship. \MarginDate{2006}
Peterhouse Travel Grant and Prizes.\\
Peterhouse Junior Scholarship. \MarginDate{2005}
Prize for Further Mathematics. \MarginDate{2004}
The George Watson Prize for Outstanding Scholarship\\ (Best Results, Class of 2004).\\
St. John Ambulance Grand Prior Award. \MarginDate{2003}
100 Hours Active Service Award, St. John Ambulance. \MarginDate{2002}
}

\vspace{1.5em}
\Heading{Publications and presentations}
\vspace{0.5em}


\SubHeading{Peer-reviewed journal articles}{}
\Description{
R. Myhill, D. McKenzie, K. Priestley, \MarginDateb{2010} ``Clustering of deep focus earthquakes in the southwest Pacific''. \\
\emph{Submitted to EPSL.}\\
R. Myhill, \MarginDateb{2008} ``Constraints on evolution of the Mesohellenic Ophiolite from sub-ophiolitic metamorphic rocks''. \\
\emph{GSA Special Publication, accepted.}\\
A. Rassios, Y. Dilek, R. Myhill, D. Ghikas, A. Mpatsi, \MarginDateb{2008} ``Melange Formations beneath the Pindos Basin Ophiolites, Northern Greece: Evidence of an “active,” rapid decollement emplacement surface''. \\
\emph{GSA Special Publication, accepted.}
}

\Sep

\SubHeading{Presentations}{}
\Description{
``Clustering of deep focus \MarginDateb{2009} earthquakes in the southwest Pacific''. \emph{Poster presentation, AGU Fall Meeting.}\\
``Faulting 300 kilometers down: \MarginDateb{2009} The mystery of deep focus earthquakes''. \emph{Magdalene Parlour Talk.}\\
``Deep focus earthquakes''. \emph{First year PhD presentation.}\\
``The significance of high temperature \MarginDateb{2008} low pressure rocks beneath the Mesohellenic Ophiolite''. \emph{Poster presentation, IGME Field Symposium: Ophiolites 2008.}\\
IGME Field Symposium: Ophiolites 2008. \emph{Field Guide.}\\
K\"{o}ln undergraduate field trip to Greece. \emph{1-day Guest Field Guide.}
}

\clearpage

\vspace{1.5em}
\Heading{Research Experience}
\vspace{0.5em}


\NewWorkExperience{06/07-01/08}{Masters Thesis at}{U. Cambridge}
\Description{
This \MarginDateb{Metamorphic Development beneath the Mesohellenic Ophiolite} project involved studying the metamorphic sole beneath the Vourinos and Pindos Complexes in Northern Greece. Its primary aim was to discover the mechanisms of sole formation, and thus obduction and emplacement of the Mesohellenic Ophiolite. The project allowed me to gain further experience in fieldwork and sampling. Further to this, I developed skills including: thin section preparation, petrographic analysis, electron probe microscopy, conventional thermobarometry, THERMOCALC thermobarometry and pseudosection construction. The project concluded with the development of a novel mechanism for emplacement of the Mesohellenic Ophiolite.\\
I obtained a high First (80\%) for this project.\\
\emph{Advisor: Dr. Timothy Holland, Cambridge University.}\\
}
\Sep

\NewWorkExperience{06/06-01/07}{Bachelors Thesis at}{U. Cambridge}
\Description{
I \MarginDateb{Independent mapping project and industrial work experience: Vourinos, Northern Greece.} was part of an international team of researchers studying areas of the Vourinos Ophiolite due to be flooded in 2009. My studies concentrated on 1:5000 scale mapping of the structural geology at the base of the Vourinos Ophiolite, particularly within the underlying tectonic m\a'{e}lange.\\
I obtained the top First in the year for this project (80\%).\\
\emph{Advisors: Dr. Alan Smith, Cambridge University and Dr. Anne Rassios, Greek Institute of Geology and Mineral Exploration (IGME).}
}
\Sep

\NewWorkExperience{07/05-08/05}{British Geological Survey}{}
\Description{
This \MarginDateb{VW, Tellus Project} paid research appointment involved soil and stream sampling and record keeping, plus field mineralogical and geological identification, for part of a national environmental survey completed in 2006.\\
\emph{Advisors: Louise Ander, Sean Quigley, Sophia Passmore (British Geological Survey).}
}


\vspace{1.5em}
\Heading{Field Experience}
\vspace{0.5em}

\Description{
230 days fieldwork experience (as of 01/06/09) including:
\begin{itemize}
\item 10-days as demonstrator on the Department of Earth Sciences IA Arran Field Trip.
\item 28-days field research for my Senior (Part III) Thesis.
\item 28-days independent mapping project.
\item 28 days paid experience with the British Geological Survey.
\item 6 days as field guide for the Ophiolites 2008 Field Symposium, Northern Greece
\item Department-organised field trips and field courses.\\
\emph{(Locations include: Ireland, Greece, Dorset, Cornwall, Sedbergh, and the Isles of Arran and Skye.)}
\end{itemize}
}

\vspace{1.5em}
\Heading{Teaching Experience}
\vspace{0.5em}

\Description{
Supervisions given in the following courses: \emph{IA Geology; IB Hydrosphere, Tectonics and Structural Geology; II/III Essay Skills.}\\
Demonstrated in the following courses: \emph{IB Tectonics and Structural Geology; II/III Tectonics, Seismology (partial).}\\
Field Demonstrator: \emph{Ketton (IA), Arran (IA), Sedbergh (IB).}
}

\clearpage

\vspace{1.5em}
\Heading{Other Experience}
\vspace{0.5em}

\Description{
Treasurer, \MarginDateb{2010-2011} Magdalene Middle Common Room.\\
Duties Coordinator, Cambridge LINKS (St. John Ambulance).\\
Treasurer, Cambridge University \MarginDateb{2007-2008} Association Football League.\\
Teaching Liaison Committee Member, Department of Earth Sciences.\\
President, Sedgwick Club (Geological Society of the University of Cambridge).\\
Time Truck \MarginDateb{2006-2007} (Cambridge Geological Outreach) Committee Member.\\
Chairman, Cambridge University Association Football League.\\
Vice President, Sedgwick Club.\\
Teaching \MarginDateb{2005-2006} Liaison Committee Member, Department of Earth Sciences.\\
Volunteer \MarginDateb{2005-present} for Time Truck.\\
Team Member of Science and Engineering Experiments for Kids, Cambridge: Science Outreach for local schools.\\
Member \MarginDateb{2002-2003} of a National Engineering Team working for Shell UK.\\
}

\vspace{1.5em}
\Heading{Skills}
\vspace{0.5em}

\Description{
\begin{itemize}
\item Competent user of \LaTeX, Microsoft and Serif Office programs and basic knowledge of Access.
\item Basic knowledge of programming in C, C++, and use of the OpenGL API.
\item Working knowledge of HTML coding (including css, javascript, flash).
\item Over 300 hours experience with THERMOCALC (a thermobarometry program based on Gibbs Energy minimisation).
\item First Aid at Work due for renewal December 2012.
\item First Aider with St John Ambulance.
\item Basic Training in Manual Handling, Radio Communication, Fire Safety.
\item Enhanced CRB checked (Disclosure Number: 001077125731).
\item Attended the Advanced Undergraduate Course in Modern Greek, Cambridge (1 year; 2007-2008).
\end{itemize}
}

\vspace{1.5em}
\Description{Geology\ \ $\cdotp$\ \ Music\ \ $\cdotp$\ \ First Aid\ \ $\cdotp$\ \  Programming\ \ $\cdotp$\ \  Foreign Travel\MarginDate{Interests}}

\vspace{1.5em}
\Heading{Referees}

\Description{
\begin{multicols}{2}{
PhD project supervisor\\
Prof. Dan McKenzie\\
Bullard Laboratories,\\
University of Cambridge,\\
Madingley Rise,\\
Cambridge.\\
CB3 0EZ.\\
UNITED KINGDOM.\\
\texttt{+44 (0)1223 337191}\\
\href{mailto:mckenzie@madingley.org}{mckenzie@madingley.org}.\\
\columnbreak
Part III project supervisor\\
Dr. Timothy Holland\\
Dept. of Earth Sciences,\\
University of Cambridge,\\
Downing Street,\\
Cambridge.\\
CB2 3EQ.\\
UNITED KINGDOM.\\
\texttt{+44 (0)1223 333453}\\
\href{mailto:tjbh@esc.cam.ac.uk}{tjbh@esc.cam.ac.uk}.\\
}
\end{multicols}
}

\vfill

% FILL IN THE FULL URL TO YOUR CV
\begin{center}
{\footnotesize \href{http://www.srcf.ucam.org/~rm438/files/CV.pdf}{http://www.srcf.ucam.org/$\sim$rm438/files/CV.pdf}\\
Last updated: \today}
\end{center}



\enlargethispage{\baselineskip}
\end{cv}
\end{document}
