\documentclass{academiccv}
\hypersetup{	
  pdftitle={Robert Myhill - Curriculum Vitae},
  pdfauthor={Robert Myhill}}

\begin{document}

% Header
\forenames{Robert}
\surname{Myhill}
\address{Department of Earth Sciences \\
University of Cambridge \\
Bullard Laboratories \\
Madingley Rise \\
Cambridge, CB3 0EZ \\
UK \\}
\phone{+44 (0)7841 714164}
\fax{+44 (0)1223 360779}
\email{rm438@cam.ac.uk}
\makehead

\section*{Education}
\DateItem{Current}{PhD Research at the University of Cambridge}{\\\textit{The Mechanisms of Deep-Focus Earthquakes}\\
I am researching the causes of earthquakes occurring at depths greater than 300 km through an integrated analysis of seismic distributions, focal mechanisms and the pressure-temperature regimes within which these events occur. I will combine this analysis with geophysical modelling techniques to elucidate aspects of the interaction between subducting plates and the upper-lower mantle boundary.\\
\emph{Advisors: Dan McKenzie and Keith Priestley}.}
\vspace{0.5em}
\DateItem{2004-2008}{\textsc{MSci + BA}}{Peterhouse, University of Cambridge, Class of 2008. \\
Natural Sciences (Physical; 4 years).\\
Part III: First Class. 1/36 in Class (Geological Sciences).\\
Part II: First Class. 1/39 in Class (Geological Sciences).\\
Part IB: First Class (Maths, Stratigraphic Geology, Mineralogy, Petrology).\\
Part IA: First Class (Geology, Maths, Physics, Chemistry).
}


\section*{Selected Grants and Awards}
\DateItem{2011}{Outstanding Student Poster Award,}{Geodynamics Division (European Geophysical Union General Assembly)}
\DateItem{2010}{The Kingsley Bye-Fellowship,}{Magdalene College Cambridge.}
\DateItem{2008}{The Hugo de Balsham Prize}{for Exceptional Academic Distinction.}
\DateItem{}{The Harkness Scholarship}{(first-placed Finalist in Geological Sciences, University of Cambridge).}
\DateItem{}{The Huppert Prize in Geophysics.}{}
\DateItem{2007}{The Henry Wilkinson Cookson Senior Scholarship}{in Natural Sciences.}
\DateItem{}{The John Reekie Memorial Prize}{for the best geological fieldwork-based thesis submitted for the first degree at the Department of Earth Sciences.}
\DateItem{2005-2006}{Peterhouse Junior and Senior Scholarships.}{}
\DateItem{2005-2007}{Departmental Field Mapping Prizes}{(5 prizes, from the Arran, Sedbergh, Dorset and Cornwall and Greece Field Trips).}
\DateItem{2004}{The George Watson Prize for Outstanding Scholarship}{(Best results, Class of 2004, Sir John Leman High School).}
\DateItem{2003}{St John Ambulance Grand Prior Award.}{}

\section*{Skills}
\footnotesize{
\begin{list}{\labelitemi}{\leftmargin=0em}
\item Competent user of \href{http://www.latex-project.org/}{\LaTeX}, Microsoft and Serif Office programs.
\item Experience of FORTRAN, C, C++, Python programming languages, and use of the OpenGL API.
\item Experience in BASH and HTML scripting.
\item Over 400 hours experience with \href{http:www.metamorph.geo.unimainz.de/thermocalc/}{THERMOCALC}, and a competent user of \href{http:www.perplex.ethz.ch/}{Perple\_X} thermodynamic software.
\item Experience of \href{http:www.fenicsproject.org/}{FEniCS} finite element modelling software.
\end{list}
}

\section*{Publications and presentations}
\subsection*{Peer-reviewed journal articles}
\Paper{2011}{Myhill, R., McKenzie, D. and Priestley, K.}{Clustering of deep-focus earthquakes in the southwest Pacific}{Earth and Planetary Science Letters}
\Paper{2011}{Myhill, R.}{Constraints on evolution of the Mesohellenic Ophiolite from sub-ophiolitic metamorphic rocks}{Geological Society of America Special Publication, in press}
\Paper{2011}{Myhill, R. and Warren, L. M.}{Fault plane orientations of deep earthquakes in the Izu-Bonin-Marianas subduction zone}{Journal of Geophysical Research, in prep}

\subsection*{Presentations}
\Talk{2011}{Earthquake distributions and their relationship with structural, chemical and thermobaric heterogeneities in subducting slabs}{Poster presentation, European Geophysical Union General Assembly}
\Talk{2011}{Deep earthquakes: Observations and controls of seismic deformation in subducting slabs}{Bullard Laboratories Friday Talk}
\Talk{2010}{The search for structure: deep-focus earthquakes}{Cambridge Earth Sciences Graduate Talk}
\Talk{2009}{Clustering of deep-focus earthquakes in the southwest Pacific}{Poster presentation, American Geophysical Union Fall Meeting}
\Talk{2009}{Faulting 300 kilometers down: The mystery of deep-focus earthquakes}{Magdalene Parlour Talk}
\Talk{2009}{Deep-focus earthquakes}{Bullard Laboratories Friday Talk}
\Talk{2008}{The significance of high temperature low pressure rocks beneath the Mesohellenic Ophiolite}{Poster presentation, Institute of Geology and Mineral Exploration (IGME) Field Symposium}

\section*{Relevant Experience}
\Experience{06/07-01/08}{Masters Thesis, University of Cambridge}{Metamorphic Development beneath the Mesohellenic Ophiolite. I obtained a high First (80\%) for this project.}{Advisor: Dr. Timothy Holland, University of Cambridge}
\Experience{06/06-01/07}{Bachelors Thesis, University of Cambridge}{Independent mapping project and industrial work experience: Vourinos, Northern Greece. I obtained the top First in the year for this project (80\%).}{Advisors: Dr. Alan Smith, University of Cambridge and Dr. Anne Rassios, IGME}
\Experience{07/05-08/05}{Field geologist, British Geological Survey}{Paid appointment for the Tellus Project, part of a national environmental survey completed in 2006.}{Advisors: Louise Ander, Sean Quigley, Sophia Passmore (British Geological Survey)}
\Experience{09/08}{Field demonstrator and member of the organising team}{}{IGME Field Symposium: Ophiolites 2008}
\Experience{2008-present}{Supervisor, University of Cambridge}{}{Geology (IA), Hydrosphere (IB), Tectonics and Structural Geology (IB), Tectonics (II/III) and Revision and Essay Skills (IA/IB/II/III)}
\Experience{}{Demonstrator, University of Cambridge}{}{Tectonics and Structural Geology (IB), Tectonics (II/III) and Seismology (II/III)}
\Experience{}{Field demonstrator, University of Cambridge}{}{Ketton (IA), Arran (IA), Sedbergh (IB)}
\Experience{}{Guest field guide, University of K\"{o}ln}{}{Vourinos Ophiolite, Northern Greece}
\Experience{2005-present}{Fieldwork experience}{250+ days (as of \today) as demonstrator, field guide, employee, researcher and student.}{(Locations include: Ireland, Iceland, Greece, Dorset, Cornwall, Sedbergh, and the Isles of Arran and Skye.)}

\section*{Other Interests}
\footnotesize{
\begin{list}{\labelitemi}{\leftmargin=0em}
\item First Aid: I am presently Stores Manager for Cambridge LINKS, the student division of St John Ambulance, having been Duties Coordinator 2010-2011 and a member since 1998.
\item Outreach: I volunteer for Time Truck (the student geological outreach organisation) and also SEEK (Science and Engineering Experiments for Kids).
\item The Sedgwick Club (The University of Cambridge geological society): As an undergraduate I was president of this society, and I remain an active member.
\item Foreign travel: I particularly enjoy my time in Greece, and spent my final year at undergraduate level learning Modern Greek at the Department of Medieval and Modern Languages.
\end{list}
}
\end{document}
